### 2019-08-10 experiment.tex
Results and Conclusions
General touching up

\chapter{The CMS experiment and the LHC} \label{chap:LHCCMS}
\section{The LHC} \label{sec:LHCCMS_LHC}
The Large Hadron Collider (LHC)~\cite{ref:1748-0221/3/08/S08001} at CERN is, as the name suggests, the world's largest
and most powerful particle accelerator. It is used to collide protons as well as heavy ions, which are both examples of hadrons, hence the ``HC'' in LHC.
Experiments attached to the collider examine the collision debris, from which features of the
parent hard-scattering process may be inferred, allowing models such as those described in Chap.~\ref{chap:introduction} to be tested.

@@

In contrast to protons in the beam, secondary muons are neither narrowly nor evenly focused by the final stretch of magnets before reaching the IP.
They enter the CMS cavern traveling parallel to the beam pipe with a wide radial profile, often having a high enough
radius to hit the exterior muon chambers and calorimeters~\cite{ref:1748-0221/10/11/P11011}.
Furthermore, the transverse distribution of MIB (Fig.~\ref{fig:beamhalo_sim}) is highly anisotropic, concentrating near the
horizontal plane.

@@

Differences in a related quantity called the \textit{rapidity}, defined as
\begin{equation}
\mathrm{rapidity} = \frac{1}{2}\ln{\frac{E+p_\mathrm{L}}{E-p_{L}}},
\label{eq:rapidity}
\end{equation}
are Lorentz invariant. Particle production in LHC collisions is roughly constant as a function of rapidity~\cite{ref:lhcrun1harvest_ch3}, and because
differences in rapidity do not depend on the longitudinal speed at which one is moving, that statement is independent
of whether the collisions are observed in their own rest frame or in that of the CMS. At very high
energies, rapidity becomes approximatey equal to the \textit{pseudorapidity} $\eta$ defined by
\begin{equation}
\eta = -\ln{\tan{(\theta/2)}}.
\label{eq:pseudorapidity}
\end{equation}

@@

The \textit{trigger primitives} (TPs) sent by HCAL and ECAL are transverse energy sums recorded in calorimeter towers.
These along with some quality information are sent to Layer 1 of the calorimeter trigger,
which performs preprocessing, energy calibration, and the computation of some simple values. Layer 2 uses this information to construct
various physics objects---L1 Jets, Taus, and EGamma\footnote{With only calorimeter information, it is difficult to distinguish $e$ from $\gamma$.
In full offline event reconstruction, this classification is refined by incorporating inner tracker information.}---using simple and fast reconstruction algorithms.
Layer 2 comprises 9 parallel cards which analyze sequential events in a round-robin, ``time-multiplexed'' fashion, so as to give
each card adequate memory and processing time for each event. The demultiplexer (DeMux) organizes the resulting output and sorts the L1 objects by $p_\mathrm{T}$,
sending this information along to the GT.

@@

Van der Meer scans require dedicated LHC runs outside of normal data taking, but the calibrated luminometers continue to monitor the beam luminosity
during physics runs. The uncertainty on calibrated luminosity measurements in 2016 data taking is 2.5\%~\cite{ref:CMS-PAS-LUM-17-001}.
The data set used in this thesis corresponds to a time-integrated luminosity $L = 35.9$\,\fbinv.

>>>>

\chapter{The LHC and the CMS experiment} \label{chap:LHCCMS}
\section{The LHC} \label{sec:LHCCMS_LHC}
The Large Hadron Collider (LHC)~\cite{ref:1748-0221/3/08/S08001} at CERN is, as the name suggests, the world's largest
and most powerful particle accelerator. It is used to collide protons as well as heavy ions, which are both examples of hadrons, hence the ``HC'' in LHC.
Experiments attached to the collider examine the collision debris, from which features of the
parent hard-scattering process may be inferred, allowing models such as those described in Chap.~\ref{chap:introduction} to be tested.

@@

In contrast to protons in the beam, secondary muons are neither narrowly nor evenly focused by the final stretch of magnets before reaching the IP.
They enter the CMS cavern traveling parallel to the beam pipe with a wide radial profile, often having a high enough
radius to hit the exterior muon chambers and calorimeters~\cite{ref:1748-0221/10/11/P11011}.
Furthermore, the transverse distribution of MIB (Fig.~\ref{fig:beamhalo_sim}) is highly anisotropic, concentrating near the
horizontal plane. Every other process examined in this thesis produces a distribution of events with constant density as a function
of angle around the beamline, and so the unique angular distribution of MIB is used to estimate its likely preponderance in a set of collision
events.

@@

Differences in a related quantity called the \textit{rapidity}, defined as
\begin{equation}
\mathrm{rapidity} = \frac{1}{2}\ln{\frac{E+p_\mathrm{L}}{E-p_{L}}}
\label{eq:rapidity}
\end{equation}
are Lorentz invariant. Particle production in LHC collisions is roughly constant as a function of rapidity~\cite{ref:lhcrun1harvest_ch3}, and because
differences in rapidity do not depend on the longitudinal speed at which one is moving, that statement is independent
of whether the collisions are observed in their own rest frame or in that of the CMS. At very high
energies, rapidity becomes approximatey equal to the \textit{pseudorapidity} $\eta$ defined by
\begin{equation}
\eta = -\ln{\tan{(\theta/2)}}
\label{eq:pseudorapidity}
\end{equation}

@@

The \textit{trigger primitives} (TPs) sent by HCAL and ECAL are transverse energy sums recorded in calorimeter towers.
These along with some quality information are sent to Layer 1 of the calorimeter trigger,
which performs preprocessing, energy calibration, and the computation of some simple values. I derived energy calibrations for this trigger layer
by comparing the TP energy distributions of simulated particle samples to the true, generated energy of the particles, and finding the
multiplicative factors that would make the peaks of the TP distributions align with the true values. These multiplicative factors, shown in Fig.~\ref{fig:layer1_calibs},
were used to scale the TP energies in online data taking in 2018. Layer 2 uses the information from Layer 1 to construct
various physics objects---L1 Jets, Taus, and EGamma\footnote{With only calorimeter information, it is difficult to distinguish $e$ from $\gamma$.
In full offline event reconstruction, this classification is refined by incorporating inner tracker information.}---using simple and fast reconstruction algorithms.
Layer 2 comprises 9 parallel cards which analyze sequential events in a round-robin, ``time-multiplexed'' fashion, so as to give
each card adequate memory and processing time for each event. The demultiplexer (DeMux) organizes the resulting output and sorts the L1 objects by $p_\mathrm{T}$,
sending this information along to the GT.

\begin{figure}[hbtb]
  \begin{center}
    \includegraphics[width=0.49\textwidth]{Figures/photon_SF_3x3.pdf}
    \includegraphics[width=0.49\textwidth]{Figures/picharged_SF_5x5.pdf}
    \caption{Calibration factors derived for Layer 1 of the calorimeter trigger, used in 2018 data taking. The energy of a trigger tower is multiplied
    by the scale factor corresponding to the tower's uncalibrated $E_{T}$ (color) and to the minimum number of other towers between it and $|\eta| = 0$ (x-axis).
    Calibrations were derived separately for the ECAL (left) and HCAL (right), using simulated photons and charged pions, respectively.}
    \label{fig:layer1_calibs}
  \end{center}
\end{figure}

@@

Van der Meer scans require dedicated LHC runs outside of normal data taking, but the calibrated luminometers continue to monitor the beam luminosity
during physics runs. The uncertainty on calibrated luminosity measurements in 2016 data taking is 2.5\%~\cite{ref:CMS-PAS-LUM-17-001}.
The data set used in this thesis corresponds to a time-integrated luminosity $L = 35.9\fbinv$.

### 2019-08-10 introduction.tex
General touching up

\chapter{Introduction} \label{chap:introduction}
\section{Overview} \label{sec:introduction_overview}
The \textit{standard model} (SM; sec.~\ref{sec:introduction_standard_model}) of particle physics is our current best mathematical framework for describing the behavior
of elementary particles. The domain of applicability of the SM is quite substantial, encompassing
every well-measured fundamental interaction of every verified fundamental particle. All SM particles have been conclusively observed,
and no fundamental particles outside the SM have ever been conclusively observed. After decades of effort by thousands of researchers,
no significant deviation from SM predictions has ever been confirmed in high-energy scattering experiments~\cite{ref:CahnGoldhaber, ref:PDG}.
These efforts are extended here with studies of the relationship between two particles, \PZ\ and \Pgamma, at state-of-the-art precision
(sec.~\ref{sec:introduction_znng} and~\ref{sec:introduction_aTGC}).

@@

Specifically, this thesis presents several analyses of event yields in \textit{monophoton} final states, characterized by a single \Pgamma\ with
high transverse momentum, along with an overall transverse momentum imbalance typically of equal magnitude and opposite direction to
that of the \Pgamma. These analyses correspond to 35.9\fbinv\ of 13\unit{TeV} proton--proton (\Pp\Pp) collision data collected in 2016 by the CMS
detector at the LHC.

\section{Standard model of particle physics} \label{sec:introduction_standard_model}
The set of particles described by the SM is illustrated in Fig.~\ref{fig:sm_particles}, which
groups them according to certain fundamental characteristics.
Each particle has an intrinsic angular momentum known as \text{spin}, specified by the lower number in each square of Fig.~\ref{fig:sm_particles}.
Spin can be an integer or half-integer, according to which the particle is classified as a \textit{boson} or \textit{fermion}, respectively.
The fundamental fermions comprise six ``flavors'' of quarks---up (\Pu), down (\Pd), charm (\Pc), strange (\Ps), top (\Pt), and bottom (\Pb)---and six flavors of
leptons: electron (\Pe), muon (\Pmu), and tau (\Ptau), with three corresponding neutrinos (\Pne, \Pnmu, \Pntau).
Each of these has both a particle and an anti-particle variety; the quarks additionally come in three ``colors''.
We typically denote a particle by a letter, e.g. \Pq\ for a generic quark; its antiparticle partner has an overbar, e.g. \Paq.
The fundamental bosons comprise the \PH\ as well as the gauge bosons, in turn comprising the \PZ, photon (\Pgamma),
two \PW s distinguished by their electric charge, and eight gluons (\Pg) distinguished by a color-anticolor doublet.

@@

The particles are related to one another through various
classes of interactions, each of which has a corresponding charge whose sum must be conserved in any physical process.
The electromagnetic and weak interactions correspond to electric charge and weak isospin, respectively.
In Fig.~\ref{fig:sm_particles}, the value $Q$ of the electric charge is specified by the middle number in each square.
For quarks and leptons, weak isospin determines whether the particle is ``up-type''
(\Pu, \Pd, \Pt, \Pne, \Pnmu, \Pntau) or ``down-type'' (\Pd, \Ps, \Pb, \Pe, \Pmu, \Ptau).
Weak isospin has a corresponding value $T_{3}$: up-type fermions have $T_{3} = \mathrm{+}1/2$, down-type fermions and the \PH\ have
$T_{3} = \mathrm{-}1/2$, $W^\pm$ have $T_{3} = \pm1$, and the other bosons have $T_{3} = 0$.
The three colors carried by quarks and gluons are associated with the strong interaction, described by the theory of \textit{quantum
chromodynamics} (QCD). The preceding discussion applies to normal (i.e.\ not anti-) particles; antiparticles carry opposite values of all the
aforementioned charges.

@@

The \PB\ and $W^{i}$s also couple to the \PH, and the structure of this coupling constrains the physical states
most easily accessed by these operators, corresponding to four distinct linear combinations of
\PB\ and $W^{i}$. These combinations, which are themselves operators, are labeled \PZ, \Pgamma, \PWplus, and \PWminus,
and these are the operators describing the physical particles detected in experiments.
In this manner, the electromagnetic and weak interactions are intertwined into the \textit{electroweak} (EWK) interaction.
The conserved electric charge $Q$ emerges as the sum of $T_{3}$ with $\frac{1}{2}Y$.

@@

Their existence is instead inferred by their absence.
In a collider experiment, the vectorial momentum transverse to the beam direction, \vecpT, must sum to approximately zero in the reference frame of the
detector. The negative vector sum of \vecpT\ for all detected particles in an event is denoted \vecMET, and its magnitude \MET\ must therefore be close
to zero if all the particles in an event are reliably detected and their momenta are accurately measured. The only high-momentum SM particles that can't
be reliably detected are neutrinos, so a large value of \MET\ can be a sign of neutrino production. An event with a high-\pT\ detected photon, in which
the \vecMET\ has a large magnitude and points in a direction significantly different from that of the photon, is called a monophoton event, and it is
expected that \zinvg\ processes are the main contributors of high-\pT\ monophoton events.

@@

\subsection{Previous measurements} \label{sec:introduction_znng_previous_measurements}
Experiments at the LEP detector measured the cross section of \zinvg\ arising from $e^{\mathrm{+}}e^{\mathrm{-}}$ collisions for $\sqrt{s}$ up to \textasciitilde200 GeV.
The L3 experiment measured the cross section to be $5.1 \pm 0.3\mathrm{(stat)} \pm 0.1\mathrm{(syst)}$ $pb$ based on 175.6 $pb^{-1}$ of collision data with an average $\sqrt{s} = 188.6$ GeV, compared to an SM
prediction of $4.99 \pm 0.05\mathrm{(stat)}$~\cite{ref:j.physletb.2004.07.002}. Looking at collision data at the same $\sqrt{s}$, but with different cuts,
the OPAL experiment measured the cross section to be $2.52 \pm 0.13\mathrm{(stat)} \pm 0.05\mathrm{(syst)}$ $pb$ based on 177.3 $pb^{-1}$ of data, compared to an SM
prediction of $2.81 \pm 0.02\mathrm{(stat)}$ $pb$~\cite{}. This set of SM predictions were made up to $O(\alpha^2)$, but LO in $\alpha_\mathrm{S}$.

@@

Despite its many triumphs, GR fails---under the assumption that SM particles and their known interactions are the only sort that exist---to describe the orbits of stars in nearly every galaxy~\cite{ref:nature25767},
the average weak distortion of light by galaxies~\cite{ref:weaklensing}, the strong distortion of light by galaxy clusters~\cite{ref:mnras/stw3385}, the orbits of galaxies in galaxy clusters~\cite{ref:annurev-astro-081710-102514},
the formation of large-scale filamentary structures~\cite{ref:nature03597}, or the distribution of ripples in the cosmic microwave background (CMB) arising from big bang nucleosynthesis~\cite{ref:planck2018_cosparams}.
Each of these phenomena could be explained by the existence of an abundance of massive matter with no discernible interactions of any sort, other than gravitation.
This extends to interactions with visible light, giving rise to the name ``dark matter.''

@@

No SM particle is predicted to exhibit the behavior of DM, and this has spurred the development
of BSM theories describing new particles that could account for it~\cite{ref:s41550-017-0059, ref:j.physrep.2004.08.031, ref:annurev.nucl.54.070103.181244, ref:S1062798717000783}.
The great diversity of theories motivates general models that can potentially constrain a wide variety of specific theories simultaneously.
If DM is particulate in nature, it apparently has a substantial mass, interacts very weakly with SM particles, and is stable on cosmological timescales~\cite{}.
The models we consider here include a BSM particle satisfying each of these criteria.
All the massive, stable particles in the SM are fermionic, and these models similarly describe a fermionic DM candidate. Otherwise, the new physics
content of these models is kept to a minimum, as sufficiently large deviations from SM predictions would presumably have been detected by now.

>>>>

\chapter{Introduction} \label{chap:introduction}
\section{Overview} \label{sec:introduction_overview}
The \textit{standard model} (SM; sec.~\ref{sec:introduction_standard_model}) of particle physics is our current best mathematical framework for describing the behavior
of elementary particles. The domain of applicability of the SM is quite substantial, encompassing
every well-measured fundamental interaction of every verified fundamental particle. All SM particles have been conclusively observed,
and no fundamental particles outside the SM have ever been conclusively observed. After decades of effort by thousands of researchers,
no significant deviation from SM predictions has ever been confirmed in high-energy scattering experiments~\cite{ref:CahnGoldhaber, ref:PDG}.
These efforts are extended here with a study of the relationship between two particles, \PZ\ and \Pgamma, at state-of-the-art precision
(sec.~\ref{sec:introduction_znng}).

@@

Specifically, this thesis presents several analyses of event yields in \textit{monophoton} final states, characterized by a single \Pgamma\ with
high transverse momentum, along with an overall transverse momentum imbalance typically of equal magnitude and opposite direction to
that of the \Pgamma.

% These analyses correspond to 35.9\fbinv\ of 13\unit{TeV} proton--proton (\Pp\Pp) collision data collected in 2016 by the CMS
% detector at the LHC.

\section{Standard model of particle physics} \label{sec:introduction_standard_model}
The set of particles described by the SM is illustrated in Fig.~\ref{fig:sm_particles}, which
groups them according to certain fundamental characteristics.
Each particle has an intrinsic property known as \text{spin}, specified by the lower number in each square of Fig.~\ref{fig:sm_particles}.
Spin can be an integer or half-integer, according to which the particle is classified as a \textit{boson} or \textit{fermion}, respectively.
The fundamental fermions comprise six ``flavors'' of quarks---up (\Pu), down (\Pd), charm (\Pc), strange (\Ps), top (\Pt), and bottom (\Pb)---and six flavors of
leptons: electron (\Pe), muon (\Pmu), and tau (\Ptau), with three corresponding neutrinos (\Pne, \Pnmu, \Pntau).
Each of these has both a particle and an anti-particle variety; the quarks additionally come in three ``colors''.
We typically denote a particle by a letter, e.g. \Pq\ for a generic quark; its antiparticle partner has an overbar, e.g. \Paq.
The fundamental bosons comprise the spin-0 Higgs boson (\PH) as well as the spin-1 vector bosons, in turn comprising the \PZ, photon (\Pgamma),
two \PW s distinguished by their electric charge, and eight gluons (\Pg) distinguished by a color-anticolor doublet.

@@

Each particle carries an energy $E$ and a momentum vector $\vec{p}$ with three components (one for every orthogonal direction in space).
In any physical process, the sum of energy as well as the vector sum of momentum over every particle must be conserved.
Particles are related into each other through various
classes of interactions, each of which has a corresponding ``charge'' whose sum must also be conserved in any physical process.
The electromagnetic and weak interactions correspond to electric charge and weak isospin, respectively.
In Fig.~\ref{fig:sm_particles}, the value $Q$ of the electric charge is specified by the middle number in each square.
For quarks and leptons, the weak isospin component $T_{3}$ determines whether the particle is ``up-type''
(\Pu, \Pd, \Pt, \Pne, \Pnmu, \Pntau) or ``down-type'' (\Pd, \Ps, \Pb, \Pe, \Pmu, \Ptau).
Up-type fermions have $T_{3} = \mathrm{+}1/2$, down-type fermions and the \PH\ have
$T_{3} = \mathrm{-}1/2$, $W^\pm$ have $T_{3} = \pm1$, and the other bosons have $T_{3} = 0$.
The three colors carried by quarks and gluons are associated with the strong interaction, described by the theory of \textit{quantum
chromodynamics} (QCD). The preceding discussion applies to normal (i.e.\ not anti-) particles; antiparticles carry opposite values of all the
aforementioned charges.

@@

The \PB\ and $W^{i}$s also couple to the \PH, and the structure of this coupling constrains the physical states
most easily accessed by these operators, corresponding to four distinct linear combinations of
\PB\ and $W^{i}$. These combinations, which are themselves operators, are labeled \PZ, \Pgamma, \PWplus, and \PWminus,
and these are the operators describing the physical particles detected in experiments.
In this manner, the electromagnetic and weak interactions are intertwined into the \textit{electroweak} (EWK) interaction.
The operators of the SM Lagrangian act on mathematical objects that represent incoming and outgoing states of particle systems.
The \PH, uniquely among SM particle operators, yields a nonzero \textit{vacuum expectation value} $v$ when the incoming and outgoing states are both the zero-particle ``vacuum state''.

The charged fermions have couplings directly to the \PH\ that are directly proportional to their masses and inversely proportional to $v$. These particles are endowed
with nonzero mass by additional \textit{mass terms}, directly proportional to the fermion mass.
Without the \PH\ coupling terms, the fermion mass terms would cause the SM Lagrangian to not be invariant under general $SU(2)$ and $U(1)_{Y}$ gauge transformations.
The photon is the only one of the EWK vector bosons with no direct \PH\ coupling. The other three also have additional terms proportional to $v$
that act as mass terms; since $v$ is nonzero, these masses are nonzero. Additional mass terms for the EWK vector bosons other than the $v$ terms would break gauge invariance.
Thus, it is their coupling to the \PH\ in conjunction with the nonzero value of $v$ that gives the charged fermions and EWK vector bosons (other than the photon) their nonzero masses
while maintaining gauge invariance. Gauge invariance guarantees that the SM makes valid predictions at all energy scales, in contrast to effective theories
(e.g. sec.~\ref{sec:introduction_dm}) that only make valid predictions in some circumscribed kinematic regime. The mass terms are only readily apparent in the SM Lagrangian
under a specific choice of $SU(2)$ and $U(1)_{Y}$ gauge transformations: after fixing this choice, only a residual $U(1)$ gauge symmetry remains, corresponding to the
\Pgamma. The conserved charge $Q$ of this residual gauge symmetry---the electric charge---is the sum of $T_{3}$ with $\frac{1}{2}Y$.

@@

Neutrino production in collision events is instead inferred by the conspicuous absence of a detector signal.
In a head-on collision of LHC particle beams, the vectorial momentum transverse to the beam direction, \vecpT, must sum to approximately zero in the reference frame of the
LHC and its detectors. The negative vector sum of \vecpT\ for all detected particles in an event is denoted \vecMET, and its magnitude \MET\ must therefore also be close
to zero, if all the particles in an event are reliably detected and their momenta are accurately measured. The only high-momentum SM particles that can't
be reliably detected by the CMS experiment (Chap.~\ref{chap:LHCCMS}) are neutrinos, so a large value of \MET\ can be a sign of neutrino production. An event with a high-\pT\ detected photon, in which
the \vecMET\ has a large magnitude and points in a direction significantly different from that of the photon, is called a monophoton event, and it is
expected that \zinvg\ processes are the main contributors of high-\pT\ monophoton events.

@@

\subsection{Previous measurements} \label{sec:introduction_znng_previous_measurements}
Experiments at the LEP detector measured the cross section of \zinvg\ arising from $e^{\mathrm{+}}e^{\mathrm{-}}$ collisions for $\sqrt{s}$ up to \textasciitilde200 GeV.
The L3 experiment measured the cross section to be $5.1 \pm 0.3\mathrm{(stat)} \pm 0.1\mathrm{(syst)}$ $pb$ based on 175.6 $pb^{-1}$ of collision data with an average $\sqrt{s} = 188.6$ GeV, compared to an SM
prediction of $4.99 \pm 0.05\mathrm{(stat)}$~\cite{ref:j.physletb.2004.07.002}. Looking at collision data at the same $\sqrt{s}$, but with different cuts,
the OPAL experiment measured the cross section to be $2.52 \pm 0.13\mathrm{(stat)} \pm 0.05\mathrm{(syst)}$ $pb$ based on 177.3 $pb^{-1}$ of data, compared to an SM
prediction of $2.81 \pm 0.02\mathrm{(stat)}$ $pb$~\cite{ref:s100520000490}. This set of SM predictions were made up to $O(\alpha^2)$, but LO in $\alpha_\mathrm{S}$.

@@

Despite these many triumphs, our knowledge of fundamental physics fails---under the assumptions that GR is true, that the universe is broadly similar in every region and every
direction of space, and that SM particles and their known interactions are the only sort that exist---to describe the orbits of stars in nearly every galaxy~\cite{ref:nature25767},
the average weak distortion of light by galaxies~\cite{ref:weaklensing}, the strong distortion of light by galaxy clusters~\cite{ref:mnras/stw3385}, the orbits of galaxies in galaxy clusters~\cite{ref:annurev-astro-081710-102514},
the formation of large-scale filamentary structures~\cite{ref:nature03597}, or the distribution of ripples in the cosmic microwave background (CMB) arising from big bang nucleosynthesis~\cite{ref:planck2018_cosparams}.
Each of these phenomena could be explained by the existence of an abundance of massive matter with no discernible interactions of any sort, other than gravitation.
This includes interactions with visible light, giving rise to the name ``dark matter.''

@@

No SM particle is predicted to exhibit the behavior of DM, and this has spurred the development
of BSM theories describing new particles that could account for it~\cite{ref:s41550-017-0059, ref:j.physrep.2004.08.031, ref:annurev.nucl.54.070103.181244, ref:S1062798717000783}.
The great diversity of theories motivates general models that can potentially constrain a wide variety of specific theories simultaneously.
If DM is particulate in nature, it seemingly has a substantial mass, interacts very weakly with SM particles, and is stable on cosmological timescales\footnote{These assumptions
are characteristic of the WIMP---Weakly Interacting Massive Particle---paradigm; other possibilities (such as axions, which are relatively light) have been proposed
that violate one or more of these assumptions~\cite{ref:S1062798717000783}.}.
The models we consider here include a BSM particle satisfying each of these criteria.
All the massive, stable particles in the SM are fermionic, and these models similarly describe a fermionic DM candidate. Otherwise, the new physics
content of these models is kept to a minimum, as sufficiently large deviations from SM predictions would presumably have been detected by now.

### 2019-08-10 reconstruction.tex
General touching up

\chapter{Object reconstruction} \label{chap:reconstruction}
\section{The particle-flow algorithm} \label{sec:reconstruction_particle_flow}
The goal of the particle-flow (PF) algorithm is to reconstruct the identities and kinematic properties of all
final-state particles in an event. The CMS is the first hadron collider experiment to have successfully implemented this strategy,
owing to its precise and robust tracking systems, highly granular and hermetic calorimeters, and intense solenoidal magnetic field.
The PF algorithm is described in detail in~\cite{ref:1748-0221/12/10/P10003}.

>>>>

\chapter{Object reconstruction} \label{chap:reconstruction}
\section{The particle-flow algorithm} \label{sec:reconstruction_particle_flow}
CMS uses the \textit{particle-flow} (PF) algorithm to attempt to reconstruct the identities and kinematic properties of all final-state particles in
a collision event. CMS is the first hadron collider experiment to have successfully implemented this strategy,
owing to its precise and robust tracking systems, highly granular and hermetic calorimeters, and intense solenoidal magnetic field.
The PF algorithm is described in detail in~\cite{ref:1748-0221/12/10/P10003}.
